### 2013-09-25 MSteenhagen-CV.tex
Changed Utrecht teaching experience on CV
Updated CV September 2013 (For refs appls)

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Research \newline presentations \newline(recent)}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

\ind 2007. Teaching Assistant in Philosophy of Science. \href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}

@@

@@

\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{British Society of Aesthetics}

>>>>

\ind 2013. \href{http://www.ucl.ac.uk/ah/figs/homepage}{UCL Faculty of Arts and Humanities} Postgraduate Research Studentship. %(£36.000)

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Research \newline presentations \newline(recent)}
\medskip

\ind 2013. ``Response to Renault--Steele'' American Society of Aesthetics annual conference, Department of Philosophy, University of California at San Diego. (Invited response.)

\ind 2013. ``Unthought thoughts'' Annual conference of the European Society for Philosophy and Psychology, University of Granada, Spain.

\ind 2013. ``Looking like: response to Sethi'' Berkeley-London Graduate Conference in Philosophy, Department of Philosophy, University of California at Berkeley. (Invited response.)

\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

\ind 2007. Teaching Assistant and seminar leader in Philosophy of Science. \href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}

@@

\ind 2013--Present. Member of the Advisory Counsil, Institute of Philosophy, London.

\ind 2013--Present. Website Manager for the \href{http://www.british-aesthetics.org.uk}{British Society of Aesthetics.}

@@

\ind Non-voting member of the board of Trustees, \href{http://www.british-aesthetics.org.uk}{British Society of Aesthetics}
